Jane, John … Leslie? Algorithmic Gender Detection

### 2014-09-03 article.Rmd
Added plot

```{r}
library(gender)
library(dplyr)
```

@@

[GRAPHIC chart of changes in names – from README]
[GRAPHIC showing change in popularity of names like Madison]

>>>>

```{r}
library(genderdata)
library(gender)
library(dplyr)
library(ggplot2)
```

@@

[GRAPHIC chart of changes in names – from README]

[GRAPHIC showing change in popularity of names like Madison]

```{r}
plot_names <-  c("madison",
                 "keanu",
                 "addison",
                 "jan",
                 "sydney",
                 "morgan",
                 "leslie")

ssa_national %>%
  filter(name %in% plot_names) %>%
  mutate(proportion_female = female / (female + male)) %>%
ggplot(aes(x = year, y = proportion_female, color = name)) +
  geom_line() +
  ggtitle("Changes in selected names")

```
